### 2019-01-08 main-plos.tex
tmp macros citep, citet
linebreaks
include all chapters
figures inline
figs
tables inline
citet -> cite
title
affiliations

@@

% \floatname{algorithm}{Pseudo code}
% \renewcommand{\algorithmicrequire}{\textbf{Input:}}
% \renewcommand{\algorithmicensure}{\textbf{Output:}}
% \renewcommand{\algorithmiccomment}[1]{\hspace{1em}\emph{\{#1\}}}
%
% %\newcommand{\tss}[1]{\textsubscript{#1}}
% %\newcommand{\tSs}[1]{\textsuperscript{#1}}
%
% %%\newcommand{\texttwosuperior}{\(^2\)}  % Unicode character ²
% %\newcommand{\texttwosuperior}{\textsuperscript{2}}  % Unicode character ²
% %\newcommand{\texttimes}{\(\times\)}  % Unicode character ×
% %\newcommand{\textmu}{\(\mu\)}  % Unicode character ×
%
% \renewcommand{\vec}[1]{\mathbf{#1}}  % Vectors and matrices.

\newcommand{\citet}{\cite}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
% Please use "sentence case" for title and headings (capitalize only the first
% word in a title (or heading), the first word in a subtitle (or subheading),
% and any proper nouns).
% % \title{Machine learning of prostate MRI: towards improved non-invasive
% % prostate cancer characterization}
\textbf\newline{Machine learning of prostate MRI:\ towards improved non-invasive
prostate cancer characterization}
}
\newline
% Insert author names, affiliations and corresponding author email (do not
% include titles, positions, or degrees).
\\
%Name Surname\textsuperscript{1,2*\textcurrency},
Jussi~Toivonen\textsuperscript{1,2*},
Ileana~Montoya~Perez\textsuperscript{1,2},
Parisa~Movahedi\textsuperscript{1,2},
Harri~Merisaari\textsuperscript{1,2,3},
Marko~Pesola\textsuperscript{1},
Pekka~Taimen\textsuperscript{4},
Peter~J.~Boström\textsuperscript{5},
Jonne~Pohjankukka\textsuperscript{2},
Aida~Kiviniemi\textsuperscript{1,6},
Tapio~Pahikkala\textsuperscript{2},
Hannu~J.~Aronen\textsuperscript{1,6},
Ivan~Jambor\textsuperscript{1,7}
\\
\bigskip
%\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\textbf{1} \deptdr, \utu, \turku\\
\textbf{2} \deptft, \utu, \turku\\
\textbf{3} Turku PET Centre, \utu, \turku\\
\textbf{4} Dept.\ of Pathology, \utu{} and \tyks, \turku\\
\textbf{5} Dept.\ of Urology, \tyks, \turku\\
\textbf{6} Medical Imaging Centre of Southwest Finland, \tyks, \turku\\
\textbf{7} Dept.\ of Radiology, University of Massachusetts---Baystate,
Springfield, MA, USA\\
\bigskip

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
\input{chapters/0-abstract}

@@

%Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}

@@

%Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\include{chapters/1-introduction}
%% \include{chapters/2-methods}
%% \include{chapters/3-results}
%% \include{chapters/4-discussion}
%% \include{chapters/5-acknowledgements}
%% \include{chapters/6-tables}
%% \include{chapters/7-figures}
%% \include{chapters/8-captions}

@@

% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
% %\usepackage{latexsym}
% \usepackage[abbreviations = true]{siunitx}
% \usepackage{algorithmic, algorithm}
% %\hypersetup{colorlinks,%
% %    citecolor=blue,%
% %    filecolor=blue,%
% %    linkcolor=blue,%
% %    urlcolor=blue,%
% %    unicode
% %    }
%
% \sisetup{detect-all = true,
%   text-rm = \sffamily,
%   per-mode = symbol,
%   literal-superscript-as-power = true
%   }
% %\DeclareSIUnit \umm{\square\um}
% \modulolinenumbers[5]
%
%
%
% \hyphenation{Lii-ma-tai-nen}
%
% %\journal{Artificial Intelligence in Medicine}
% \journal{}
%
% %%%%%%%%%%%%%%%%%%%%%%%
% %% Elsevier bibliography styles
% %%%%%%%%%%%%%%%%%%%%%%%
% %% To change the style, put a % in front of the second line of the current style and
% %% remove the % from the second line of the style you would like to use.
% %%%%%%%%%%%%%%%%%%%%%%%
% %% Numbered
% \bibliographystyle{model1-num-names}
% %% Numbered without titles
% %\bibliographystyle{model1a-num-names}
% %% Harvard
% %\bibliographystyle{model2-names.bst}\biboptions{authoryear}
% %% Vancouver numbered
% %\usepackage{numcompress}\bibliographystyle{model3-num-names}
% %% Vancouver name/year
% %\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
% %% APA style
% %\bibliographystyle{model5-names}\biboptions{authoryear}
% %% AMA style
% %\usepackage{numcompress}\bibliographystyle{model6-num-names}
% %% `Elsevier LaTeX' style
% %\bibliographystyle{elsarticle-num}
% %%%%%%%%%%%%%%%%%%%%%%%
%
% \begin{document}
%
% \begin{frontmatter}
%
%
%
% \begin{abstract}
% \end{abstract}
%
% \begin{keyword}
% MRI \sep prostate cancer \sep texture analysis \sep
% Gleason score classification \sep computer-aided diagnostics
% %\MSC[2010] 00-01\sep  99-00
% \end{keyword}
%
% \end{frontmatter}
%
% \linenumbers
%
% \end{document}

>>>>

% JPT: Additional packages
\usepackage{algorithmic, algorithm}

@@

\floatname{algorithm}{Pseudo code}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\renewcommand{\algorithmiccomment}[1]{\hspace{1em}\emph{\{#1\}}}

% %\newcommand{\tss}[1]{\textsubscript{#1}}
% %\newcommand{\tSs}[1]{\textsuperscript{#1}}
%
% %%\newcommand{\texttwosuperior}{\(^2\)}  % Unicode character ²
% %\newcommand{\texttwosuperior}{\textsuperscript{2}}  % Unicode character ²
% %\newcommand{\texttimes}{\(\times\)}  % Unicode character ×
% %\newcommand{\textmu}{\(\mu\)}

\renewcommand{\vec}[1]{\mathbf{#1}}  % Vectors and matrices.
\newcommand{\ci}[1]{{\small (#1)}}  % CI range for the AUCs.

% TODO
\newcommand{\citep}{\cite}
%\newcommand{\citet}[1]{TODO:{#1}~\cite{#1}}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
% Please use "sentence case" for title and headings (capitalize only the first
% word in a title (or heading), the first word in a subtitle (or subheading),
% and any proper nouns).
% % \title{Machine learning of prostate MRI: towards improved non-invasive
% % prostate cancer characterization}
\textbf\newline{Radiomics and machine learning of multisequence multiparametric
prostate MRI:\ towards improved non-invasive prostate cancer characterization}
}
\newline
% Insert author names, affiliations and corresponding author email (do not
% include titles, positions, or degrees).
\\
%Name Surname\textsuperscript{1,2*\textcurrency},
Jussi~Toivonen\textsuperscript{1,2*},
Ileana~Montoya~Perez\textsuperscript{1,2},
Parisa~Movahedi\textsuperscript{1,2},
Harri~Merisaari\textsuperscript{1,2,3},
Marko~Pesola\textsuperscript{1},
Pekka~Taimen\textsuperscript{4},
Peter~J.~Boström\textsuperscript{5},
Jonne~Pohjankukka\textsuperscript{2},
Aida~Kiviniemi\textsuperscript{1,6},
Tapio~Pahikkala\textsuperscript{2},
Hannu~J.~Aronen\textsuperscript{1,6},
Ivan~Jambor\textsuperscript{1,7}
\\
\bigskip
%\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\textbf{1} \deptdr, \utu, \turku\\
\textbf{2} \deptft, \utu, \turku\\
\textbf{3} Turku PET Centre, \utu, \turku\\
\textbf{4} Institute of Biomedicine, \utu{} and
    Dept.\ of Pathology, \tyks, \turku\\
\textbf{5} Dept.\ of Urology, \tyks, \turku\\
\textbf{6} Medical Imaging Centre of Southwest Finland, \tyks, \turku\\
\textbf{7} Diagnostic Radiology, Icahn School of Medicine at Mount Sinai, New
    York, NY, USA\\
\bigskip

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta
%erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante
%cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend
%volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar
%non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
%Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet
%enim ultrices, ultrices elit pulvinar, volutpat risus.
\input{chapters/0-abstract}

@@

%Figure caption text here, please use this space for the figure panel
%descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit
%amet. B: Consectetur adipiscing elit.}

@@

%Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et
%malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac
%quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam
%rhoncus vitae.

\include{chapters/1-introduction}
\include{chapters/2-methods}
\include{chapters/3-results}
\include{chapters/4-discussion}
\include{chapters/5-acknowledgements}
\include{chapters/8-captions}

@@

% %\usepackage{latexsym}
% \usepackage[abbreviations = true]{siunitx}
% %\hypersetup{colorlinks,%
% %    citecolor=blue,%
% %    filecolor=blue,%
% %    linkcolor=blue,%
% %    urlcolor=blue,%
% %    unicode
% %    }
%
% \sisetup{detect-all = true,
%   text-rm = \sffamily,
%   per-mode = symbol,
%   literal-superscript-as-power = true
%   }
% %\DeclareSIUnit \umm{\square\um}
% \modulolinenumbers[5]
%
%
%
% \hyphenation{Lii-ma-tai-nen}
%
% %\journal{Artificial Intelligence in Medicine}
% \journal{}
%
% %%%%%%%%%%%%%%%%%%%%%%%
% %% Elsevier bibliography styles
% %%%%%%%%%%%%%%%%%%%%%%%
% %% To change the style, put a % in front of the second line of the current style and
% %% remove the % from the second line of the style you would like to use.
% %%%%%%%%%%%%%%%%%%%%%%%
% %% Numbered
% \bibliographystyle{model1-num-names}
% %% Numbered without titles
% %\bibliographystyle{model1a-num-names}
% %% Harvard
% %\bibliographystyle{model2-names.bst}\biboptions{authoryear}
% %% Vancouver numbered
% %\usepackage{numcompress}\bibliographystyle{model3-num-names}
% %% Vancouver name/year
% %\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
% %% APA style
% %\bibliographystyle{model5-names}\biboptions{authoryear}
% %% AMA style
% %\usepackage{numcompress}\bibliographystyle{model6-num-names}
% %% `Elsevier LaTeX' style
% %\bibliographystyle{elsarticle-num}
% %%%%%%%%%%%%%%%%%%%%%%%
%
% \begin{document}
%
% \begin{frontmatter}
%
%
%
% \begin{abstract}
% \end{abstract}
%
% \begin{keyword}
% MRI \sep prostate cancer \sep texture analysis \sep
% Gleason score classification \sep computer-aided diagnostics
% %\MSC[2010] 00-01\sep  99-00
% \end{keyword}
%
% \end{frontmatter}
%
% \linenumbers
%
% \end{document}
